% TestTensor

\pentry{词条示例\upref{Sample}}

The word "tensor" first appeared in Structural Mechanics, used to describe the properties of stress, therefore translated as “张力”. The term continues in use until today, except the translation now becomes “张量”. Today we realize that the stress tensor is only a particular case for a more general mathematical object, tenosr. This object appears in corners in physics frequently. We will define the concept of tensor from the fundamental sense, which is the contemporary perspective. We will also demonstrate how a tensor is represented by a matrix or a high dimensional matrix. 

This section is a step-by-step guiding textbook, rather than a list of concepts and theorems. To better understand this section, it is recommended that the reader have solid understanding of linear algebra. 

The definition we use in this section is the most fundamental version. No additional structures or constraints are put onto it; also, Einstein's Summation Agreement is not applied yet, so as to be friendly for beginners. For the common concepts like covariant or contravariant tensors, please refer to the subsequent sections. 



\subsection{Introduction}

A tensor is a multi-linear map. Particularly, a second-order tensor can be interpreted as a map from two vectors to a scalor, or a map from a vector to another vector. The scalor here refers to an element in the field that defines the vector space; in physics, the field is usually the real numbers or the complex numbers. 

Many physical quantities can be interpreted as linear maps. As an example, mass is a second-order tensor, which maps a force vector to an acceleration vector; the moment of inertia is a second-order tensor, which maps an angular velocity vector to an angular momentum vector. Tensors of different orders may behave differently, but they all share one property: the linearity. When you encounter tensors in the future, I suggest you take some time and think "what quantities does this tensor map from and to"; it helps a deeper understanding. 



\subsection{1-linear function, 2-linear function and their representation}

It is known that given 2 vector spaces $V$ and $W$, we can define a linear map from $V$ to $W$. In this case, we have only 1 independent and 1 dependent variables. A multi-linear map, say, a k-linear map, maps a series of vector spaces $V_1, V_2, \cdots, V_k$ to $W$, so that if only the element in one $V_i$ varies, the map varies in the way a linear map does. 

The simplest case is when $W$ is a 1-dimensional space. In this case, the vector space $W$ is also the field (the real numbers). If the image of a map is some set of numbers, then we have a particular term for such a map, \textbf{function}. This is the same function that you may have seen in high school, as the maps involved in high school are mostly from real numbers to real numbers. Now, since we make $W$ the set of real numbers, we just call the map from $V_1, V_2, \cdots, V_k$ to $W$ a \textbf{linear function}. Now, we are going to introduce the concepts of multi-linear maps, tensors and their representations, step by step, starting with linear functions. 

\subsubsection{Representing linear functions with vectors}

\begin{definition}{Linear functions}
Given the n-dimensional vector space $V$ on $\mathbb{R}$, we call $f:V\rightarrow \mathbb{R}$ a \textbf{linear function} from $V$ to $\mathbb{R}$, if and only if $f$ satisfies the linearity: for any vectors $\bvec{v}_1, \bvec{v}_2\in V$ and scalors $a_1, a_2\in\mathbb{R}$, we have: $a_1f(\bvec{v}_1)+a_2f(\bvec{v}_2)=f(a_1\bvec{v}_1+a_2\bvec{v}_2)$．
\end{definition}


\end{definition}

If we think of $\mathbb{R}$ as a 1-dimensional vector space, then $f$ is a linear map from $V$ onto this vector space. Therefore, if we take any base of $V$ and determine what real numbers $f$ maps the base vectors to, then we can calculate $f(\bvec{v})$ for any vector $\bvec{v}\in V$. 

Now suppose a base of $V$ is $\{\bvec{e}_i\}^n_{i=1}$. If the base vector $\bvec{e}_i$ is mapped to $f(\bvec{e}_i)=m_i\in\mathbb{R}$, then for any vector $\bvec{v}=a_1\bvec{e}_1+a_2\bvec{e}_2+\cdots+a_n\bvec{e}_n$, we can calculate by linearity: 

\begin{equation}
\begin{aligned}
f(a_1\bvec{e}_1+a_2\bvec{e}_2+\cdots+a_n\bvec{e}_n)&=f(a_1\bvec{e}_1)+f(a_2\bvec{e}_2)+\cdots+f(a_n\bvec{e}_n)\\&=m_1a_1+m_2a_2+\cdots+m_na_n
\end{aligned}
\end{equation}


$m_1a_1+m_2a_2+\cdots+m_na_n$can be interpreted as the inner product of $\bvec{m}$ and $\bvec{v}$, where$\bvec{m}=m_1\bvec{e}_1+m_2\bvec{e}_2+\cdots+m_n\bvec{e}_n$．

That is, every linear function $f$ corresponds to a vector $\bvec{m}$, so that $f(\bvec{v})=\bvec{m}\cdot\bvec{v}$．The coordinate of the vector $\bvec{m}$, in the base $\{\bvec{e}_i\}_{i=1}^n$, is $(m_1, m_2, \cdots, m_n)^T$. If we define another base, the coordinate usually changes, but the vector is still the same. 

Since a linear function is a map from a vector space to real numbers, we also call it a 1-linear function. It is to distinguish it from other multi-linear functions, like the 2-linear function we are going to focus on now. 

\subsubsection{Representing 2-linear funcions with matices}

Let's stick to the n-dimensional vector space $V$, except now we take 2 copies of $V$ to construct the map $f:V\times V\rightarrow\mathbb{R}$．

\begin{definition}{2-linear function}
We call $f:V\times V\rightarrow\mathbb{R}$ a 2-linear function, if and only if for any fixed vector $\bvec{v}_0$, both $f(\bvec{v}_0, \bvec{v})$ and $f(\bvec{v}, \bvec{v}_0)$ are 1-linear functions for $\bvec{v}$. In particular, we call $f$ a 2-linear function from $(V, V)$ onto $\mathbb{R}$. 
\end{definition}

An explicit expression for a 2-linear function is as follows: 

\begin{equation}\label{TestT_eq2}
\begin{aligned}
f(a_1\bvec{v}_1+a_2\bvec{v}_2, b_1\bvec{u}_1+b_2\bvec{u}_2)&=a_1f(\bvec{v}_1, b_1\bvec{u}_1+b_2\bvec{u}_2)+a_2f(\bvec{v}_2, b_1\bvec{u}_1+b_2\bvec{u}_2)\\&=a_1b_1f(\bvec{v}_1, \bvec{u}_1)+a_2b_1f(\bvec{v}_2, \bvec{u}_1)+a_1b_2f(\bvec{v}_1, \bvec{u}_2)+a_2b_2f(\bvec{v}_2, \bvec{u}_2)
\end{aligned}
\end{equation}


In order to represent this map, we have to determine the bases for the two copies of $V$. They don't have to be the same base. Let's assume the base for the first $V$ is $\{\bvec{e}_i\}^n_{i=1}$, and for the second is $\{\bvec{e}_i'\}^n_{i=1}$. Now vectors in the two vector spaces can be represented by column matrices, and the 2-linear function by a square matrix: (example with a 2-dimesional $V$)
\begin{equation}\label{TestT_eq1}
\begin{aligned}
&\bvec{v}=a_1\bvec{e}_1+a_2\bvec{e}_2\rightarrow  \bvec c_v=\pmat{a_1\\a_2}\\
&\bvec{u}=b_1\bvec{e}'_1+b_2\bvec{e}'_2\rightarrow  \bvec c_u=\pmat{b_1\\b_2}\\
&f\rightarrow \bvec{M}=\pmat{f(\bvec{e}_1, \bvec{e}'_1)&f(\bvec{e}_1, \bvec{e}'_2)\\f(\bvec{e}_2, \bvec{e}'_1)&f(\bvec{e}_2, \bvec{e}'_2)}\\
\end{aligned}
\end{equation}


That way, we have $f(\bvec{v}, \bvec{u})= \bvec c_v^T\bvec{M} \bvec c_u$．Note that $\bvec c_v^T$ means the transpose of the matix $\bvec c_v$\footnote{If we use other bases, then the representations of $\bvec{v}$, $\bvec{u}$ and $f$ may be different matrices, but the calculation of $\bvec c_v^T\bvec{M} \bvec c_u$ doesn't change}．

\begin{exercise}{}
Think of the coordinate of a vector as a column matrix, then use to the laws of matrix calculation and substitute \autoref{TestT_eq1} into \autoref{TestT_eq2} to verify that $f(\bvec{v}, \bvec{u})= \bvec c_v^T\bvec{M} \bvec c_u$．
\end{exercise}


The example we just talked about is for 2-dimensional $V$. For n-dimensional $V$, $\bvec{M}$ becomes a $n\times n$ matrix, where the element in the ith row and jth column is $m_{ij}=f(\bvec{e}_i, \bvec{e}'_j)$．

我们来看一个简单的$2$-线性函数的例子．

\begin{example}{功率}
三维空间里一个物体的受力，可以构成一个三维实线性空间$V$，这个物体的速度，也可以构成一个$V$\footnote{回忆：$\mathbb{R}$上的线性空间，只要维度相同，都可以看成同一个空间．}．用$\bvec{F}$表示物体受到的力，$\bvec{v}$表示物体的速度，那么这个力对物体做功的功率$P$就是一个双线性函数：$P=\bvec{F}\cdot\bvec{v}$．如果选定了受力空间和速度空间的基，还可以把向量$\bvec{F}$和$\bvec{v}$分别表示成列向量$c_F$和$c_v$，那么就有$P=c^T_F\bvec{P}c_v$，这里的$\bvec{P}$就是一个双线性函数，它的作用是表示功率的计算方式．如果我们按以下方式选择基：受力空间的基是沿着$x$、$y$和$z$方向的大小为$1N$的力，而速度空间的基是沿着$x$、$y$和$z$方向的大小为$1\opn{m/s}$的速度，那么在这两组基下，表示功率的双线性函数的矩阵就是单位矩阵$\pmat{1&0&0\\0&1&0\\0&0&1}$；如果把受力空间的基改为沿着$y$、$x$和$z$方向，那么表示功率的双线性函数的矩阵就变成了$\pmat{0&1&0\\1&0&0\\0&0&1}$．此时，如果\textbf{再}把速度空间的基改为沿着$x$、$z$和$y$方向，那么功率函数的矩阵就变成了$\pmat{0&0&1\\1&0&0\\0&1&0}$．
\end{example}




